Quantum Interval-Valued Probability: Measurement and Probability

### 2017-11-25 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

Before discussing quantum IVPMs, we first review various notations
brought forward from conventional quantum theory. Assume that a physical
system is represented by a density matrix~$\rho$, and that we wish
to measure a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectral decomposition is given by
$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
projector onto the eigenspace of the eigenvalue~$\lambda_{i}$. Then,
the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
is given by~\cite{544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
\end{equation}

@@

\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
decomposition~(\ref{eq:spectrum-decomposition}). A subspace of events~$\events'\subseteq\events$
is called a subspace of events induced by $\mathbf{O}$ if it is the
minimal subspace of events satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
Obvious, $\events'$ is convex.\end{definition}

Notice that a sub-event space induced by any observable commutes.
By theorem~\ref{thm:sub-event-space}, we can find a set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$ to pull quantum
real-valued or interval-valued probability measures to classical ones.
Although it is a powerful tool, it would be more powerful if we can
pull an observable to a random variable as well.

\begin{definition}\label{def:observable2random-variable}Given an
observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition})
and its inducing subspace of events\nb$\events'$, set~$\Omega$,
and function~$\tau:\events'\rightarrow2^{\Omega}$. Then, the random
variable~$X:\Omega\rightarrow\mathbb{R}$ defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$
is called the random variable induced by $\mathbf{O}$.\end{definition}

>>>>

Before discussing quantum IVPMs, we first review various notations
brought forward from conventional quantum theory. Assume that a physical
system is represented by a density matrix~$\rho$, and that we wish
to measure a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectral decomposition is given by
\begin{equation}
\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}\,,\label{eq:spectrum-decomposition}
\end{equation}
where $P_{i}$ is the projector onto the eigenspace of each distinct
eigenvalue~$\lambda_{i}$. Since $\lambda_{i}$ are distinct, $N$
may be less than $d$. Although we requires the eigenvalues in a spectral
decomposition to be distinct, we will relax this requirement in the
next section. Then, the Born rule of CQT tells us that the expectation
value of the observable~$\mathbf{O}$ is given by~\cite{544199,Jaeger2007}
\begin{equation}
\expval{\mathbf{O}}_{\mu_{\rho}^{\mathrm{B}}}=\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .\label{eq:quantum-expectation}
\end{equation}

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition-distinct}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
\end{equation}

@@

\begin{definition}Given an observable~$\mathbf{O}$ with any its
spectral decomposition~(\ref{eq:spectrum-decomposition}) whose eigenvalues
are not necessary distinct. A subspace of events~$\events'\subseteq\events$
is called consistent with $\mathbf{O}$ if it is the minimal subspace
of events satisfying $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$.
Obviously, $\events'$ is commuting and convex.\end{definition}

By theorem~\ref{thm:sub-event-space}, we can find a set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$ to pull quantum
real-valued or interval-valued probability measures to classical ones.
Although it is a powerful tool, it would be more powerful if we can
pull an observable to a random variable as well.

\begin{definition}\label{def:observable2random-variable}Given an
observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition-distinct})
and its inducing subspace of events\nb$\events'$, set~$\Omega$,
and function~$\tau:\events'\rightarrow2^{\Omega}$. Then, the random
variable~$X:\Omega\rightarrow\mathbb{R}$ defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$
is called the random variable induced by $\mathbf{O}$.\end{definition}
